\Large \includegraphics[height=\baselineskip]{title.png} \\ \vspace{0.65mm} \large \normalfont CSE 227: Computer Security - Spring 2017 \\ \textit{ University of California San Diego }

### 2017-06-14 docs/paper.tex
IDNs

\abstract{
The introduction of Internationalized Domain Names (IDNs) made access the web easier to non-English speakers.
However, it also opened up the possibility of using homograph domain names maliciously, in what has been called IDN homograph attacks.
This kind of attack can be used to trick users into thinking they are visiting a different (but homograph) domain name.
Our approach to analyze its potential impact was based on clustering internationalized domain names with their counterparts in the Alexa Top 1m web sites ranking.
The results obtained indicate that there are more than a thousand (at least) IDN homographs among \textit{.com} domains.
While most of them are not being used actively, they still possess a potential security risk as there are no guarantees they will remain inactive in the future.
}

@@

\section{Introduction}
Domain names were originally designed to only support ASCII characters.
Internationalized Domain Names (IDNs) were proposed back in December 1996 by Martin D\"{u}rst\endnote{\url{https://tools.ietf.org/html/draft-duerst-dns-i18n-00}} for the purpose of letting non-English speakers use Internet without additional restrictions.
This extension involves representing Unicode characters in ASCII using Punycode, so that they could be then rendered back into their Unicode representation.
Homograph letters (different letters whose representation is almost, if not, the same), however, present a potential security vulnerability.
For example, Cyrillic letter ``a'' can look identical to Latin letter ``a'' depending on the font.
In other languages, like Chinese, there exist many homograph letters between traditional Chinese and simplified Chinese.
Malicious attackers could then register a domain where one of the letters is actually Cyrillic but whose representation matched a Latin one.
Users could be linked to this newly registered malicious page, and they may not have any visual indication (at least without further interaction) that the page is not the one they think they are visiting.

In this paper, we analyze the potential impact of this type of attack, commonly referred to as IDN homograph attack.
Section 2 explains past and present policies of major browsers and top-level domain (TLD) registrants in an attempt to prevent the attack.
Section 3 explores relevant work in the literature related to homograph attacks.
Section 4 describes the methodology of data collection and analysis adopted in this project.
Section 5 comments the different results obtained.
Section 6 addresses the ethical concerns regarding the data collection.
Section 7 presents the conclusions obtained from this project.

@@

\section{Related Work}
Several relevant studies have been conducted to describe the potential security issues with internationalized domain names, while providing possible solutions to mitigate the surface attack of these homograph domain names. The first of these studies, \textit{The Homograph Attack}~\cite{gabrilovich2002}, was written by Evgeniy Gabrilovich and Alex Gontmakher in 2001, and proved the feasability of the attack.

@@

Other attempts to analyze the impact of homograph attacks have also been made.
In 2009, Peter Hanay and Christopher Bolan~\cite{hannay2009} concluded that, while most modern browsers in fact have implemented useful measures to prevent internationalized domain name homograph attacks, email clients where not nearly as effective, specially when dealing with incoming emails.
In 2010, Johnny Al Helou and Scott Tilley~\cite{al2010} argued that the introduction of country-code Top Level Domains (ccTLDs) have made this attack easier to perform again.

Our approach to analyze the potential security risk of homograph internationalized domain names was fundamentally different the ones evaluated.
Rather than inspecting traffic or generating random homograph permutations of a string, we took a more systematic approach.
We clustered all internationalized homograph domains using a snapshot of the \texttt{.com} domain zone.
We then used a list of top web sites and domain registrants data to classify each homograph domain name.

@@

\subsection{Data Processing}
We used the \textit{.com snapshot} to obtain all the internationalized domains of the \texttt{.com} domain zone.
All internationalized domain names are represented using Punycode, so they start with the \texttt{xn--} prefix.
Using this information we first filtered the \textit{.com snapshot} to match only the \texttt{.com} domains that start with \texttt{xn--}.
Since the \textit{.com snapshot} contains name server records, a single domain may have more than one entry in the file.
Only the domain name is relevant for this project, so the rest of the columns of the \textit{.com snapshot} were discarded.
We sorted the domains in lexicographical order, removing duplicates in the process.

We used the \textit{top domains snapshot} as a source for the canonical (non-international) domain name of a website, based on its ranking.
As we were only interested in non-internationalized domain names, we discarded the ones that start with the prefix \texttt{xn--}.
We also removed sub-domains, since we only had top-level domain names in the \textit{.com snapshot}.

\subsection{Clustering}
The underlying assumptions behind the clustering process are that homograph attacks are more likely to target popular domains, and that the million domains from the \textit{top domains snapshot} contains most of the popular domains.
To detect potential internationalized domain name homograph attacks, we clustered the internationalized domain names in the \textit{.com snapshot}.
The representative of each cluster is a homograph domain name from the \textit{top domains snapshot}, which we called canonical domain name.
Only clusters with at least one internationalized homograph domain name were output.

@@

\begin{table*}[b!]
\centering
\begin{tabular}{lrr}
\hline
Domains                                           & \#                         & \%                         \\ \hline
\itshape\sffamily{Canonical domain names}         & \itshape\sffamily{458731}  & \itshape\sffamily{8.31\%}  \\
\hspace{0.5cm} With IDN homographs                & 825                        & 6.04\%                     \\
\hspace{0.5cm} Without IDN homographs             & 457906                     & 2.27\%                     \\
\itshape\sffamily{Internationalized Domain Names} & \itshape\sffamily{1045400} & \itshape\sffamily{91.69\%} \\
\hspace{0.5cm} With canonical homograph           & 1099                       & 3.68\%                     \\
\hspace{0.5cm} Without canonical homograph        & 1044301                    & 2.74\%                     \\ \hline
\end{tabular}
\caption{Overview of the clustering results.}
\label{clustering-results}
\end{table*}

@@

\section{Results}
We obtained 458731 domain names from the \textit{top domains snapshot} that belonged to the \texttt{.com} zone.
From the \textit{.com snapshot}, we identified a total of 1044301 internationalized domains.
However, only a low percentage of the internationalized domain names (3.68\%) had a matching homograph canonical domain name in the \textit{top domains snapshot}.
Even if we take into account that our homograph detection algorithm is rather limited (as described before), these results still indicate that the majority of internationalized domain names are not being used in homograph attacks.
An overview of these clustering results can be found in Table~\ref{clustering-results}.

@@

The manual classification sheds some light on how these homograph internationalized domain names are currently being used.
For the most part (82.34\%), the domains are registered by a third party, and not being used actively (parking).
One possible explanation for this is that the domain was bought in an attempt to be re-sold later at a higher price to the owner of the matching canonical homograph domain.
However, the potential security risk is still present as there are no guarantees that the parked domains will remain inactive in the future.
A detailed breakdown of this classification can be found in Table~\ref{manually-classified-idns}.

Table~\ref{top-registrants-homograph-idns} contains the top ten registrants with the most homograph internationalized domain names.
Most of these registrants are actually domain privacy companies, so it is impossible to know if the domains belong to the same person or not.
There are also several individuals with a high number of homograph internationalized domain names.
It is also worth mentioning that some of these individuals seem to be targeting specific industries.
For instance, a single person has registered homographs of ``audi'', ``citroen'' and ``diesel''.

\section{Ethical Considerations}
The domain information used in this project is publicly available, and was voluntarily provided by the registrants of the domains when they registered them.
The full \texttt{.com} domain zone snapshot will not be publicly disclosed, as its access requires a paid subscription.
The retrieval of the \textit{WHOIS} information was performed only for the homograph internationalized domain names, which were about one thousand.
It was performed with a significant delay between petitions (3 seconds) in order to avoid saturating the servers.

@@

\clearpage

>>>>

\abstract{
The introduction of Internationalized Domain Names (IDNs) made access the web easier to non-English speakers.
However, it also opened up the possibility of using homograph domain names maliciously, in what has been called IDN homograph attacks.
This kind of attack can be used to trick users into thinking they are visiting a different (but homograph) domain name.
Our approach to analyze its potential impact was based on clustering IDNs with their canonical counterparts in the Alexa Top 1m web sites ranking.
The results obtained indicate that there are more than a thousand (at least) IDN homographs among \textit{.com} domains.
While most of them are not being used actively, they still possess a potential security risk as there are no guarantees they will remain inactive in the future.
}

@@

\section{Introduction}
Domain names were originally designed to only support ASCII characters.
IDNs were proposed back in December 1996 by Martin D\"{u}rst\endnote{\url{https://tools.ietf.org/html/draft-duerst-dns-i18n-00}} for the purpose of letting non-English speakers use Internet without additional restrictions.
This extension involves representing Unicode characters in ASCII using Punycode, so that they could be then rendered back into their Unicode representation.
Homograph letters (different letters whose representation is almost, if not, the same), however, present a potential security vulnerability.
For example, Cyrillic letter ``a'' can look identical to Latin letter ``a'' depending on the font.
In other languages, like Chinese, there exist many homograph letters between traditional Chinese and simplified Chinese.
Malicious attackers could then register a domain where one of the letters is actually Cyrillic but whose representation matched a Latin one.
Users could be linked to this newly registered malicious page, and they may not have any visual indication (at least without further interaction) that the page is not the one they think they are visiting.

In this paper, we analyze the potential impact of this type of attack, commonly referred to as IDN homograph attack.
Section 2 explains past and present policies of major browsers and domain registrars in an attempt to prevent the attack.
Section 3 explores relevant work in the literature related to homograph attacks.
Section 4 describes the methodology of data collection and analysis adopted in this project.
Section 5 comments the different results obtained.
Section 6 addresses the ethical concerns regarding the data collection.
Section 7 presents the conclusions obtained from this project.

@@

\section{Related Work}
Several relevant studies have been conducted to describe the potential security issues with IDNs, while providing possible solutions to mitigate the surface attack of these homograph domain names. The first of these studies, \textit{The Homograph Attack}~\cite{gabrilovich2002}, was written by Evgeniy Gabrilovich and Alex Gontmakher in 2001, and proved the feasability of the attack.

@@

Other attempts to analyze the impact of homograph attacks have also been made.
In 2009, Peter Hanay and Christopher Bolan~\cite{hannay2009} concluded that, while most modern browsers in fact have implemented useful measures to prevent internationalized domain name homograph attacks, email clients where not nearly as effective, specially when dealing with incoming emails.
In 2010, Johnny Al Helou and Scott Tilley~\cite{al2010} argued that the introduction of ccTLDs have made this attack easier to perform again.

Our approach to analyze the potential security risk of homograph IDNs was fundamentally different the ones evaluated.
Rather than inspecting traffic or generating random homograph permutations of a string, we took a more systematic approach.
We clustered all internationalized homograph domains using a snapshot of the \texttt{.com} domain zone.
We then used a list of top web sites and domain registrants data to classify each homograph domain name.

@@

\subsection{Data Processing}
We used the \textit{.com snapshot} to obtain all the internationalized domains of the \texttt{.com} domain zone.
All IDNs are represented using Punycode, so they start with the \texttt{xn--} prefix.
Using this information we first filtered the \textit{.com snapshot} to match only the \texttt{.com} domains that start with \texttt{xn--}.
Since the \textit{.com snapshot} contains name server records, a single domain may have more than one entry in the file.
Only the domain name is relevant for this project, so the rest of the columns of the \textit{.com snapshot} were discarded.
We sorted the domains in lexicographical order, removing duplicates in the process.

We used the \textit{top domains snapshot} as a source for the canonical (non-international) domain name of a website, based on its ranking.
As we were only interested in non-IDNs, we discarded the ones that start with the prefix \texttt{xn--}.
We also removed sub-domains, since we only had second level domain names in the \textit{.com snapshot}.

\subsection{Clustering}
The underlying assumptions behind the clustering process are that homograph attacks are more likely to target popular domains, and that the million domains from the \textit{top domains snapshot} contains most of the popular domains.
To detect potential internationalized domain name homograph attacks, we clustered the IDNs in the \textit{.com snapshot}.
The representative of each cluster is a homograph domain name from the \textit{top domains snapshot}, which we called canonical domain name.
Only clusters with at least one internationalized homograph domain name were output.

@@

\begin{table*}[b!]
\centering
\begin{tabular}{lrr}
\hline
Domains                                           & \#                         & \%                         \\ \hline
\itshape\sffamily{Canonical domain names}         & \itshape\sffamily{458731}  & \itshape\sffamily{8.31\%}  \\
\hspace{0.5cm} With IDN homographs                & 825                        & 6.04\%                     \\
\hspace{0.5cm} Without IDN homographs             & 457906                     & 2.27\%                     \\
\itshape\sffamily{IDNs} & \itshape\sffamily{1045400} & \itshape\sffamily{91.69\%} \\
\hspace{0.5cm} With canonical homograph           & 1099                       & 3.68\%                     \\
\hspace{0.5cm} Without canonical homograph        & 1044301                    & 2.74\%                     \\ \hline
\end{tabular}
\caption{Overview of the clustering results.}
\label{clustering-results}
\end{table*}

@@

\section{Results}
We obtained 458731 domain names from the \textit{top domains snapshot} that belonged to the \texttt{.com} zone.
From the \textit{.com snapshot}, we identified a total of 1044301 internationalized domains.
However, only a low percentage of the IDNs (3.68\%) had a matching homograph canonical domain name in the \textit{top domains snapshot}.
Even if we take into account that our homograph detection algorithm is rather limited (as described before), these results still indicate that the majority of IDNs are not being used in homograph attacks.
An overview of these clustering results can be found in Table~\ref{clustering-results}.

@@

The manual classification sheds some light on how these homograph IDNs are currently being used.
For the most part (82.34\%), the domains are registered by a third party, and not being used actively (parking).
One possible explanation for this is that the domain was bought in an attempt to be re-sold later at a higher price to the owner of the matching canonical homograph domain.
However, the potential security risk is still present as there are no guarantees that the parked domains will remain inactive in the future.
A detailed breakdown of this classification can be found in Table~\ref{manually-classified-idns}.

Table~\ref{top-registrants-homograph-idns} contains the top ten registrants with the most homograph IDNs.
Most of these registrants are actually domain privacy companies, so it is impossible to know if the domains belong to the same person or not.
There are also several individuals with a high number of homograph IDNs.
It is also worth mentioning that some of these individuals seem to be targeting specific industries.
For instance, a single person has registered homographs of ``audi'', ``citroen'' and ``diesel''.

\section{Ethical Considerations}
The domain information used in this project is publicly available, and was voluntarily provided by the registrants of the domains when they registered them.
The full \texttt{.com} domain zone snapshot will not be publicly disclosed, as its access requires a paid subscription.
The retrieval of the \textit{WHOIS} information was performed only for the homograph IDNs, which were about one thousand.
It was performed with a significant delay between petitions (3 seconds) in order to avoid saturating the servers.

@@
